### 2024-06-04 skripsi/bab3.tex
remove ignored files
change to biblatex, start background

\section{Model Komputasi}
\noindent The DeepONet architecture contains an element that is difficult to optimize.
% \begin{mini}
%   {W_b}{y=(W_b\cdot f+b_b)^\top\cdot(W_t\cdot v+b_t)+\xi
% \end{mini}

\begin{mini!}|s|
{\substack{W_b,b_b,W_t,b_t,\xi}}{\frac{1}{2}\Vert W_b\Vert_F^2 + \frac{1}{2}\Vert W_t\Vert_F^2 + \frac{c}{2}\sum_{i=1}^{l}\xi_i^2} {}{}
\addConstraint{y_i}{=(W_b f_i+b_b)^\top(W_t v_i+b_t)+\xi_i,\quad}{i=1,\ldots,l}
\end{mini!}

@@

    L(W_b,b_b,W_t,b_t,\xi;\alpha)= {} & \frac{1}{2}\Vert W_b\Vert_F^2 + \frac{1}{2}\Vert W_t\Vert_F^2 +\frac{c}{2}\sum_{i=1}^{l}\xi_i^2 \\ &+ \sum_{i=1}^{l}\alpha_i(y_i-\xi_i-(W_b f_i+b_b)^\top(W_t v_i+b_t))

@@

>>>>

\section{Computational Model}
\noindent The proposed model derives inspiration from DeepONet, Neural Spectral methods, and Spectral Neural Operators. The method uses LSSVR to map between the input coefficients/functions and the solution coefficients. This mapping is the surrogate of the operator in the spectral domain. To exploit the nature of the problem, the kernel chosen has particular characteristics that makes it useful for the spectral/function domain. These are kernels such as the maximum distance between two functions or something that lies in the spectral domain favoring low/high frequencies depending on the particular problem.
% \begin{mini}
%   {W_b}{y=(W_b\cdot f+b_b)^\top\cdot(W_t\cdot v+b_t)+\xi
% \end{mini}

\begin{mini!}|s|
{\substack{\vb*{W_b},\vb*{W_t},\vb*{\xi}}}{\frac{1}{2}\Vert \vb*{W_b}\Vert_F^2 + \frac{1}{2}\Vert \vb*{W_t}\Vert_F^2 + \frac{c}{2}\sum_{i=1}^{N}\xi_i^2} {}{}
\addConstraint{y_i}{=(\vb*{W_b} \vb*{f_i})^\top(\vb*{W_t} \vb*{v_i})+\xi_i,\quad}{i=1,\ldots,N}
\end{mini!}
Converting the optimization problem above to the lagrange formulation

@@

    L(\vb*{W_b},\vb*{W_t},\vb*{\xi};\vb*{\alpha})= {} & \frac{1}{2}\Vert \vb*{W_b}\Vert_F^2 + \frac{1}{2}\Vert \vb*{W_t}\Vert_F^2 +\frac{c}{2}\sum_{i=1}^{N}\xi_i^2 \\ &+ \sum_{i=1}^{N}\alpha_i(y_i-\xi_i-(\vb*{W_b} \vb*{f_i})^\top(\vb*{W_t} \vb*{v_i}))

@@

Taking partial derivatives with respect to 

### 2024-06-04 skripsi/sampuldalam.tex
change to biblatex, start background

\textbf{\MakeUppercase{\large tugas akhir}}\\[0.5cm]
\begin{onehalfspace}
Diajukan untuk memenuhi syarat kelulusan tahap pendidikan strata-1 pada\\
Program Studi Fisika -- Institut Teknologi Bandung\\[1.8cm]
\end{onehalfspace}

\large Oleh: \\
\begin{onehalfspace}
\large{\penulis} \\
\large{\nim}\\[1.5cm]
\end{onehalfspace}
\vspace{1.5cm}

% EDIT PEMBIMBING, udah deh sampul2. :D
\large Pembimbing: \\
\begin{onehalfspace}
\large{\pembimbingsatu} \\
\large{\pembimbingdua}
\end{onehalfspace}

@@

% bagian bawah
\textbf{\large \MakeUppercase{program studi fisika}}\\
\textbf{\large \MakeUppercase{fakultas matematika dan ilmu pengetahuan alam}}\\
\textbf{\large \MakeUppercase{institut teknologi bandung}}\\
\textbf{\large 2021}\\
\end{center}

>>>>

\textbf{\MakeUppercase{\large A Research Paper}}\\[0.5cm]
\begin{onehalfspace}
Submitted as partial fulfillment of the requirements for \textit{sarjana komputer} degree at\\
Program Studi Ilmu Komputer -- Universitas Pendidikan Indonesia\\[1.8cm]
\end{onehalfspace}

\large By: \\
\begin{onehalfspace}
\large{\penulis} \\
\large{\nim}\\[1.5cm]
\end{onehalfspace}
\vspace{1.5cm}

% EDIT PEMBIMBING, udah deh sampul2. :D
\large Supervisors: \\
\begin{onehalfspace}
\large{\pembimbingsatu} \\
\large{\pembimbingdua}
\end{onehalfspace}

@@

% bagian bawah
\textbf{\MakeUppercase{program studi ilmu komputer}}\\
\textbf{ \MakeUppercase{fakultas pendidikan matematika dan ilmu pengetahuan alam}}\\
\textbf{\MakeUppercase{UNIVERSITAS PENDIDIKAN INDONESIA}}\\
\textbf{\the\year{}}\\
\end{center}
